\textbf{Predicting virus-receptor mutant binding by molecular dynamics simulation}

### 2013-07-17 paper.tex
last minor edits.

The hTfR1 is the primary receptor used by MACV for binding its host cell prior to infection. The primary role of hTfR1 $in~vivo$ is to bind transferrin for cellular iron uptake. The hTfR1 protein contains three extracellular domains: two basilar domains and an apical domain. The two basilar domains serve most of the transferrin-binding function \citep{Abraham2010,Rad20112}. Viral entry is initiated by GP1 binding to the apical domain of hTfR1. Previous work has indicated that the GP1/hTfR1 binding interaction is the primary determinant of MACV host range variation \citep{Rad20111,Rad20112}. The co-crystal structure shows the high affinity interaction between GP1 and hTfR1 forces the normally flexible loop in the apical domain of hTfR1 into a rigid beta-pleated sheet domain. For GP1, several extended loops in mediate binding to hTfR1 \citep{Abraham2010,Rad20112}, and many of the interface interactions are mediated by extensive hydrogen-bonding networks \citep{Abraham2010}. Experimental alanine-scanning and whole cell infectivity assays have identified several sites in both GP1 and hTfR1 that are probably critical for establishing infection \citep{Rad20111,Rad20112}.

@@

The python packages MDAnalysis \citep{Agrawal2011} and ProDy \citep{Bakan2011} were both used at various points in post-processing. The molecular trajectory (comprising the atomic coordinates per time) was parsed to compute the center-of-mass for each of the two complexes. The starting center-of-mass distance was set to zero and the distance was re-computed at each time step relative to the starting distance. The force is output directly to the standard log file.

@@

For our experiments, we used the experimentally determined GP1/hTfR1 structure (PDBID: 3KAS) \citep{Abraham2010}. The apical domain of hTfR1 interacts directly with GP1 while the other two domains are closer to the cell membrane and have essentially no interaction with GP1. The biophysical independence of the apical domain allowed us to isolate it without significantly affecting the GP1/hTfR1 interaction. Figure~\ref{fig:protein_comparison} shows a model of the initial structure and that of the pared structure. Although GP1 has several glycosylatable residues, we opted to use the de-glycosylated protein for this study. The complexity of correctly parameterizing diverse sugar moieties is outside of the scope of this paper. Furthermore, although it is known that GP1 is glycosylated, and some of those sugars contact hTfR1, the effect of those contacts \textit{in vivo} is still unresolved \citep{Abraham2010}.

In total, we tested 7 point mutants and 3 double mutants in addition to the WT complex (Table~\ref{tab:summary_mutants} and Figure~\ref{fig:mutant_comparison}). Mutations at site hTfR1 site 211 have proven capable of causing loss-of-entry according to \textit{in vitro} flow-cytometry infection assays or known host-range limitations \citep{Rad2008,Rad20111,Rad20112}. Most likely, this effect is caused by the destruction of a critical hydrogen bond to Ser113 or Ser111 in GP1. The lost hydrogen bond would lead to the subsequent loss of a large hydrogen-bonding network seen in the crystal structure (Table~\ref{tab:summary_mutants}) \citep{Abraham2010}. In a manner similar to site 211, Asn348 appears to be important for binding by participating in a critical hydrogen bonding network \citep{Rad2008,Abraham2010} to GP1. In particular, Asn348Lys is reported in the literature to cause significantly reduced viral entry \textit{in vivo} (Table~\ref{tab:summary_mutants}) \citep{Rad2008,Abraham2010}. Finally, an alanine mutation at site 111 in GP1 has also been shown to cause decreased entry (Table~\ref{tab:summary_mutants}) \citep{Rad20112}. For notation purposes, the viral site is always referred to with a preceding `v'.

\subsection*{Steered molecular dynamics simulations}
To ensure a natural solution structure, we performed an initial equilibration phase to reduce the intrinsic crystallization distortions. First, we generated a physically realistic simulation world around the protein complex. The environment included an explicitly modeled bath of water, and a physiologically relevant concentration of ions. Next, we carried out successive rounds of energy minimization with a fixed $\alpha$-carbon backbone, followed by heating, and backbone release. Last, we performed a short round of all-atom molecular dynamics with minimal restraints \citep{Cuendet2008}. We used the final state from each equilibrated system to restart another MD simulation. For SMD, at the centroid of several atoms a force was applied to a single point in GP1. By using a known spring constant, and pulling with a constant velocity, we could calculate the applied force during protein--protein dissociation \citep{Cuendet2008,Cuendet2011}. A typical averaged force curve comparison can be seen in Figure~\ref{fig:force_curve}. The force curves for each mutant were smoothed either by averaging over many replicates as in Figure~\ref{fig:force_curve} or by selecting an interpolation window for averaging. The latter approach was used for statistical analysis. In addition, to minimize the computational time in unproductive molecular dynamics, we shortened the simulation time such that the interaction just barely dropped to zero near the end of each run. As seen in Figure~\ref{fig:force_curve}, this distance was relatively consistent among mutants. The supplementary movie visually illustrates the separation distance between peptide domains. The quantities maximum applied force and AUC were derived from the force versus distances curves. Their summary statistics are reported in Table~\ref{tab:summary_statistics}. As we are more interested in the phenotypic impact of interface mutations we avoided many of the more physically rigorous, but technically complicated calculations that are possible with SMD \citep{Is2001A,Is2001B}.

@@

We found that relative to WT, one alanine mutation (Tyr211Ala) produced a very large and statistically significant difference in the maximum applied force and AUC (Figure~\ref{fig:force_curve}, Table~\ref{tab:MAF_pairwise}), while the other two did not (Table~\ref{tab:MAF_pairwise}). When considering additional mutants (also discussed below), we found that maximum applied force was generally sufficient to distinguish mutants (Tables~\ref{tab:MAF_pairwise} and ~\ref{tab:MAF_p}), and AUC was able to add a few more statistically significant differences (Table~\ref{tab:AUC_p}). In general, however, maximum applied force seemed to be the more sensitive statistic than AUC.

\subsection*{Comparative analysis of the GP1/hTfR1 interface}
Considering the involvement of extended hydrogen-bonding networks in the GP1/hTfR1 interface, it was not clear that individual alanine mutations, even those that should destroy such networks, would significantly change the strength of interaction. One major advantage of first principles simulations is the ability to test mutations other than alanine without additional underlying assumptions in the energy function. Seen in Table~\ref{tab:summary_mutants}, we made additional mutations based on biochemical intuition or available experimental data to chemically diverse amino acids including tryptophan, lysine, aspartate, and threonine. Several mutations caused significant relative affinity changes. In addition, to detect synergistic effects, we tested several double mutants where both mutations appeared to cause similar changes in binding. Then, we compared the size of those differences to single mutants (Figure~\ref{fig:sensitivity} and ~\ref{fig:mutant_comparison}).

Although Tyr211Ala appears to have a large impact on binding affinity, no single mutant can provide enough evidence to understand the biochemical difference in binding mechanism. Since alanine is both smaller than tyrosine and also incapable of participating in hydrogen-bond interactions, we tested further mutations to identify the critical biochemical difference responsible for change in binding affinity. In particular, we substituted smaller side chains that, like tyrosine, were capable of hydrogen bonding. We chose Tyr211Asp and Tyr211Thr, two mutations that have been discussed in the context of selection pressure on hosts in rodent populations \citep{Rad2008,Rad20111,Rad20112}. Both mutations proved capable of causing a significant change in binding affinity in our simulations, but the change appeared to be increased affinity (Figure~\ref{fig:sensitivity} and ~\ref{fig:mutant_comparison}, and Table~\ref{tab:MAF_p}).

We also simulated several point mutations at Asn348 in the hTfR1. As discussed above, the alanine mutation at this site showed no significant difference in maximum applied force or AUC from WT (Tables~\ref{tab:MAF_p} and ~\ref{tab:AUC_p}). In addition, neither the Asn348Lys nor the Asn348Trp mutation showed a significant difference from WT. For both of these mutations, however, mean maximum applied force and mean AUC was lower than for WT (See Table~\ref{tab:summary_statistics}).  On the other hand, there was a detectable difference between Asn348Ala and Asn348Lys (Tables~\ref{tab:MAF_p} and~\ref{tab:AUC_p}), with Asn348Lys being a weaker binder. Moreover, Asn348Trp showed nearly identical results to Asn348Lys. The mutations to large amino acids (Asn348Trp and Asn348Lys) produced nearly identical affinity changes, whereas the mutations to amino acids not capable of hydrogen bonding (Asn348Ala and Asn348Trp) produced significantly different affinity changes (Table~\ref{tab:MAF_pairwise}). To check the consistency of our results, we hypothesized that the combination of Tyr211Ala and Asn348Trp, being chemically disconnected in two different hydrogen-bonding networks, would lead to a synergistic loss-of-binding. As expected, the double mutant was the weakest binding mutant tested ($ p < 10^{-6} $) (Tables~\ref{tab:MAF_p} and~\ref{tab:AUC_p}) in this study. Further, according to maximum applied force (but not AUC), the combination of Tyr211Ala and Asn348Trp also showed significantly weaker binding than Tyr211Ala by itself (Tables~\ref{tab:MAF_p} and~\ref{tab:AUC_p}). We suspect that the effect of Asn348Trp alone is near the limit of detection using our method. A larger number of replicates would possibly have resolved affinity differences between Asn348Trp and WT or other mutants more consistently.

@@

We have applied a method utilizing steering forces in all-atom molecular dynamics simulations to evaluate the effects of mutations at the GP1/hTfR1 interface. We modeled mutations at several sites in the GP1/hTfR1 interface, and verified that our computational protocol was sensitive enough to distinguish point mutants in hTfR1. Further, we identified two test statistics, maximum applied force and AUC, that can be used as proxies for binding affinity. We systematically tested several point mutations to understand their contribution to the binding interaction. In the case of Asn348Lys, we have shown that the static structure provides little insight into why this mutation causes loss-of-infectivity \textit{in vivo}. While Asn348 appears to be involved in a hydrogen-bonding network in the static structure, change in binding at that site may actually be caused by size and charge restriction. We also found that a negatively polar residue at site 211 in hTfR1 is absolutely critical for a tight binding interaction. Any non-polar mutation at Tyr211 in hTfR1 is likely to completely halt viral entry and dramatically decrease the chances of MACV infection.

@@

Our findings may rationalize several effects observed in both infectivity data and rodent populations \citep{Rad2008,Rad20111}. First, we found that some substitutions at positions 211 and 348 did affect the strength of receptor binding. However, the computational data suggest that the reason and nature of the effects at these two sites are very different. At position 211, mutations to non-polar residues causes a large change in binding. This is congruent with what is known from viral entry data \citep{Rad2008,Rad20111}. By contrast, mutations at position 348 need only be small to maintain WT binding. The ability to hydrogen bond appears to be insignificant. This can be inferred from the fact that Tyr211Ala paired with large (Trp) and positively charged (Lys) substitutions at position 348 results in a larger than expected synergistic difference. That is, the double mutant Tyr211Ala/Asn348Trp caused a much larger decrease in binding than we expected from either mutation individually. Third, the GP1 mutation vArg111Ala causes a loss-of-infection during \textit{in vitro} infectivity assays \citep{Rad20112}, yet it was indistinguishable from the WT complex in our simulations. Although Tyr211Ala was the most disruptive single mutant we tested, vArg111Ala in the GP1 was able to restore mean maximum applied force to WT levels (Table~\ref{tab:summary_statistics}), and to levels significantly higher than observed for Tyr211Ala alone.

We would like to emphasize here that we cannot expect perfect agreement. While we have shown that our method can distinguish individual point mutations, we do not know the limit of detection with our method. First, it is possible that some mutants display measurable phenotypic effects in experiments yet appear identical under our method. More extensive sampling or refinement of the simulation protocol could help to differentiate such mutants (see also next paragraph). Second, our SMD method is fundamentally a measurement tool, and as a result we are dramatically limited by the accuracy of our starting structure. Third, the available experimental data for the GP1/hTfR1 system were generally obtained from entry assays or whole-cell binding assays rather than molecular binding assays. A mutant may cause a phenotypic difference in infectivity without generating a signal by our method. For example, entry could be lost in the experimental system because the protein is grossly or partially misfolded. An additional analytical step with circular dichroism or an analogous technique could clarify such large-scale folding differences. Further, since our simulations start with a bound structure, any changes that may dramatically affect the rate of association (different folds, trafficking issues, etc.) or relative orientation of the two proteins would be underestimated by our method. Finally, it is tempting to think only decreased binding affinity should correlate strongly with diminished infectivity. However, dramatically increased binding affinity could also disrupt infectivity by prohibiting cellular membrane detachment after viral invasion. The virus would be prevented from reaching its replication compartment (which is the cytosol in the case of Machupo) and could not reproduce.

@@

\clearpage
\begin{figure}[p]
\centerline{\includegraphics[width=6in]{figures/mutant_comparison_boxplot.pdf}}
\caption{\label{fig:mutant_comparison}\title{Distribution of interpolated maximum force for all complexes tested.} The statistically significant difference relative to the WT complex are indicated by a star above the distribution.}
\end{figure}

\clearpage
\begin {table}[H]
\caption{\label{tab:summary_mutants}Summary of information for each mutation tested. Observed $in~vivo$ refers to mutations that have been observed in rodent populations. Phenotype $in~vitro$ refers to the observed phenotype in $in~vitro$ viral entry assays.} 
\begin{center}
  \resizebox{11cm}{!} {
    \begin{tabular}{l c r r}
    \hline
      Mutation & Observed $in~vivo$ & Phenotype $in~vitro$ \\
            WT &                Yes &         Normal Entry \\
         N348A &                 No &                    - \\
         N348K &                Yes &     Diminished Entry \\
         N348W &                 No &                    - \\
         Y211A &                 No &        No Expression \\
         Y211D &                Yes &        No Expression \\
         Y211T &                 No &     Diminished Entry \\
        vR111A &                 No &     Diminished Entry \\
   N348A/Y211A &                 No &                    - \\
   N348W/Y211A &                 No &                    - \\
  vR111A/Y211A &                 No &                    - \\
    \hline
    \end{tabular}
  }
\end{center}
\end{table}

>>>>

The hTfR1 is the primary receptor used by MACV for binding its host cell prior to infection. The primary role of hTfR1 $in~vivo$ is to bind transferrin for cellular iron uptake. The hTfR1 protein contains three extracellular domains: two basilar domains and an apical domain. The two basilar domains serve most of the transferrin-binding function \citep{Abraham2010,Rad20112}. Viral entry is initiated by GP1 binding to the apical domain of hTfR1. Previous work has indicated that the GP1/hTfR1 binding interaction is the primary determinant of MACV host range variation \citep{Rad20111,Rad20112}. The co-crystal structure shows the high affinity interaction between GP1 and hTfR1 forces the normally flexible loop in the apical domain of hTfR1 into a rigid beta-pleated sheet domain. For GP1, several extended loops mediate binding to hTfR1 \citep{Abraham2010,Rad20112}, and many of the interface interactions are mediated by extensive hydrogen-bonding networks \citep{Abraham2010}. Experimental alanine-scanning and whole-cell infectivity assays have identified several sites in both GP1 and hTfR1 that are probably critical for establishing infection \citep{Rad20111,Rad20112}.

@@

The python packages MDAnalysis \citep{Agrawal2011} and ProDy \citep{Bakan2011} were both used at various points in post-processing. The molecular trajectory (comprising the atomic coordinates per time) was parsed to compute the center-of-mass for each of the two complexes. The starting center-of-mass distance was set to zero and the distance was re-computed at each time step relative to the starting distance. The force was output directly to the standard log file.

@@

For our experiments, we used the experimentally determined GP1/hTfR1 structure (PDBID: 3KAS) \citep{Abraham2010}. The apical domain of hTfR1 interacts directly with GP1 while the other two domains are closer to the cell membrane and have essentially no interaction with GP1. The biophysical independence of the apical domain allowed us to isolate it without significantly affecting the GP1/hTfR1 interaction. Figure~\ref{fig:protein_comparison} shows a model of the initial structure and that of the pared structure. Although GP1 has several glycosylatable residues, we opted to use the de-glycosylated protein for this study. The complexity of correctly parameterizing diverse sugar moieties is outside of the scope of this paper. Furthermore, although it is known that GP1 is glycosylated, and some of those sugars contact hTfR1, the sugars in the available PDB structure are not physiological for mammals \citep{Abraham2010}.

In total, we tested 7 point mutants and 3 double mutants in addition to the WT complex (Table~\ref{tab:summary_mutants} and Figure~\ref{fig:mutant_comparison}). Mutations at site hTfR1 site 211 have proven capable of causing loss-of-entry according to \textit{in vitro} flow-cytometry infection assays or known host-range limitations \citep{Rad2008,Rad20111,Rad20112}. Most likely, this effect is caused by the destruction of a critical hydrogen bond to Ser113 or Ser111 in GP1. The lost hydrogen bond would lead to the subsequent loss of a large hydrogen-bonding network seen in the crystal structure (Table~\ref{tab:summary_mutants}) \citep{Abraham2010}. In a manner similar to site 211, Asn348 appears to be important for binding by participating in a critical hydrogen bonding network \citep{Rad2008,Abraham2010} to GP1. In particular, Asn348Lys is reported in the literature to cause significantly reduced viral entry \textit{in vivo} (Table~\ref{tab:summary_mutants}) \citep{Rad2008,Abraham2010}. Finally, an alanine mutation at site 111 in GP1 (mutation vArg111Ala) has also been shown to cause decreased entry (Table~\ref{tab:summary_mutants}) \citep{Rad20112}. For notation purposes, the viral site is always referred to with a preceding `v'.

\subsection*{Steered molecular dynamics simulations}

We proceeded to analyze this system using molecular dynamics. To ensure a natural solution structure, we performed an initial equilibration phase to reduce the intrinsic crystallization distortions. First, we generated a physically realistic simulation world around the protein complex. The environment included an explicitly modeled bath of water, and a physiologically relevant concentration of ions. Next, we carried out successive rounds of energy minimization with a fixed $\alpha$-carbon backbone, followed by heating, and backbone release. Last, we performed a short round of all-atom molecular dynamics with minimal restraints \citep{Cuendet2008}. We used the final state from each equilibrated system to restart another MD simulation. For SMD, at the centroid of several atoms a force was applied to a single point in GP1. By using a known spring constant, and pulling with a constant velocity, we could calculate the applied force during protein--protein dissociation \citep{Cuendet2008,Cuendet2011}. A typical averaged force curve comparison can be seen in Figure~\ref{fig:force_curve}. The force curves for each mutant were smoothed either by averaging over many replicates as in Figure~\ref{fig:force_curve} or by selecting an interpolation window for averaging. The latter approach was used for statistical analysis. In addition, to minimize the computational time in unproductive molecular dynamics, we shortened the simulation time such that the interaction just barely dropped to zero near the end of each run. As seen in Figure~\ref{fig:force_curve}, this distance was relatively consistent among mutants. The supplementary movie visually illustrates the separation distance between peptide domains. The quantities maximum applied force and AUC were derived from the force versus distances curves. Their summary statistics are reported in Table~\ref{tab:summary_statistics}. As we are more interested in the phenotypic impact of interface mutations we avoided many of the more physically rigorous, but technically complicated calculations that are possible with SMD \citep{Is2001A,Is2001B}.

@@

We found that relative to WT, one alanine mutation (Tyr211Ala) produced a very large and statistically significant difference in the maximum applied force and AUC (Figure~\ref{fig:force_curve}, Table~\ref{tab:MAF_pairwise}), while the other two did not (Table~\ref{tab:MAF_pairwise}). When considering additional mutants (also discussed below), we found that maximum applied force was generally sufficient to distinguish mutants (Tables~\ref{tab:MAF_pairwise} and~\ref{tab:MAF_p}), and AUC was able to add a few more statistically significant differences (Table~\ref{tab:AUC_p}). In general, however, maximum applied force seemed to be the more sensitive statistic than AUC.

\subsection*{Comparative analysis of the GP1/hTfR1 interface}
Considering the involvement of extended hydrogen-bonding networks in the GP1/hTfR1 interface, it was not clear that individual alanine mutations, even those that should destroy such networks, would significantly change the strength of interaction. One major advantage of first principles simulations is the ability to test mutations other than alanine without additional underlying assumptions in the energy function. As shown in Table~\ref{tab:summary_mutants}, we made additional mutations based on biochemical intuition or available experimental data to chemically diverse amino acids including tryptophan, lysine, aspartate, and threonine. Several mutations caused significant relative affinity changes. In addition, to detect synergistic effects, we tested several double mutants where both mutations appeared to cause similar changes in binding. Then, we compared the size of those differences to single mutants (Figure~\ref{fig:sensitivity} and~\ref{fig:mutant_comparison}).

Although Tyr211Ala appears to have a large impact on binding affinity, no single mutant can provide enough evidence to understand the biochemical difference in binding mechanism. Since alanine is both smaller than tyrosine and also incapable of participating in hydrogen-bond interactions, we tested further mutations to identify the critical biochemical difference responsible for change in binding affinity. In particular, we substituted smaller side chains that, like tyrosine, were capable of hydrogen bonding. We chose Tyr211Asp and Tyr211Thr, two mutations that have been discussed in the context of selection pressure on hosts in rodent populations \citep{Rad2008,Rad20111,Rad20112}. Both mutations proved capable of causing a significant change in binding affinity in our simulations, but the change appeared to be increased affinity (Figures~\ref{fig:sensitivity} and~\ref{fig:mutant_comparison}, and Table~\ref{tab:MAF_p}).

We also simulated several point mutations at Asn348 in the hTfR1. As discussed above, the alanine mutation at this site showed no significant difference in maximum applied force or AUC from WT (Tables~\ref{tab:MAF_p} and~\ref{tab:AUC_p}). In addition, neither the Asn348Lys nor the Asn348Trp mutation showed a significant difference from WT. For both of these mutations, however, mean maximum applied force and mean AUC was lower than for WT (See Table~\ref{tab:summary_statistics}).  On the other hand, there was a detectable difference between Asn348Ala and Asn348Lys (Tables~\ref{tab:MAF_p} and~\ref{tab:AUC_p}), with Asn348Lys being a weaker binder. Moreover, Asn348Trp showed nearly identical results to Asn348Lys. The mutations to large amino acids (Asn348Trp and Asn348Lys) produced nearly identical affinity changes, whereas the mutations to amino acids not capable of hydrogen bonding (Asn348Ala and Asn348Trp) produced significantly different affinity changes (Table~\ref{tab:MAF_pairwise}). To check the consistency of our results, we hypothesized that the combination of Tyr211Ala and Asn348Trp, being chemically disconnected in two different hydrogen-bonding networks, would lead to a synergistic loss-of-binding. As expected, the double mutant was the weakest binding mutant tested ($ p < 10^{-6} $, Tables~\ref{tab:MAF_p} and~\ref{tab:AUC_p}) in this study. Further, according to maximum applied force (but not AUC), the combination of Tyr211Ala and Asn348Trp also showed significantly weaker binding than Tyr211Ala by itself (Tables~\ref{tab:MAF_p} and~\ref{tab:AUC_p}). We suspect that the effect of Asn348Trp alone is near the limit of detection using our method. A larger number of replicates would possibly have resolved affinity differences between Asn348Trp and WT or other mutants more consistently.

@@

We have applied a method utilizing steering forces in all-atom molecular dynamics simulations to evaluate the effects of mutations at the GP1/hTfR1 interface. We modeled mutations at several sites in the GP1/hTfR1 interface, and verified that our computational protocol was sensitive enough to distinguish point mutants in hTfR1. Further, we identified two test statistics, maximum applied force and AUC, that can be used as proxies for binding affinity. We systematically tested several point mutations to understand their contribution to the binding interaction. In the case of Asn348Lys, we have shown that the static structure provides little insight into why this mutation causes loss-of-infectivity \textit{in vivo}. While Asn348 appears to be involved in a hydrogen-bonding network in the static structure, change in binding at that site may actually be caused by size and charge restriction. We also found that a negatively polar residue at site 211 in hTfR1 seem critical for a tight binding interaction. Any non-polar mutation at Tyr211 in hTfR1 is likely to completely halt viral entry and dramatically decrease the chances of MACV infection.

@@

Our findings may rationalize several effects observed in both infectivity data and rodent populations \citep{Rad2008,Rad20111}. First, we found that some substitutions at positions 211 and 348 did affect the strength of receptor binding. However, the computational data suggest that the reason and nature of the effects at these two sites are very different. At position 211, mutations to non-polar residues cause a large change in binding. This is congruent with what is known from viral entry data \citep{Rad2008,Rad20111}. By contrast, mutations at position 348 need only be small to maintain WT binding. The ability to hydrogen bond appears to be insignificant. This can be inferred from the fact that Tyr211Ala paired with large (Trp) and positively charged (Lys) substitutions at position 348 results in a larger than expected synergistic difference. That is, the double mutant Tyr211Ala/Asn348Trp caused a much larger decrease in binding than we expected from either mutation individually. Third, the GP1 mutation vArg111Ala causes a loss-of-infection during \textit{in vitro} infectivity assays \citep{Rad20112}, yet it was indistinguishable from the WT complex in our simulations. Although Tyr211Ala was the most disruptive single mutant we tested, vArg111Ala in the GP1 was able to restore mean maximum applied force to WT levels (Table~\ref{tab:summary_statistics}), and to levels significantly higher than observed for Tyr211Ala alone.

We would like to emphasize here that we cannot expect perfect agreement between our simulations and the available experimental data. While we have shown that our method can distinguish individual point mutations, we do not know the limit of detection with our method. First, it is possible that some mutants display measurable phenotypic effects in experiments yet appear identical under our method. More extensive sampling or refinement of the simulation protocol could help to differentiate such mutants (see also next paragraph). Second, our SMD method is fundamentally limited by the accuracy of our starting structure. Third, the available experimental data for the GP1/hTfR1 system were generally obtained from entry assays or whole-cell binding assays rather than molecular binding assays. A mutant may cause a phenotypic difference in infectivity without generating a signal by our method. For example, entry could be lost in the experimental system because the protein is grossly or partially misfolded. An additional analytical step with circular dichroism or an analogous technique could clarify such large-scale folding differences. Further, since our simulations start with a bound structure, any changes that may dramatically affect the rate of association (different folds, trafficking issues, etc.) or relative orientation of the two proteins would be underestimated by our method. Finally, it is tempting to think only decreased binding affinity should correlate strongly with diminished infectivity. However, dramatically increased binding affinity could also disrupt infectivity by prohibiting cellular membrane detachment after viral invasion. The virus would be prevented from reaching its replication compartment (which is the cytosol in the case of Machupo) and could not reproduce.

@@

\clearpage
\begin{figure}[p]
\centerline{\includegraphics[width=6in]{figures/mutant_comparison_boxplot.pdf}}
\caption{\label{fig:mutant_comparison}\title{Distribution of interpolated maximum force for all complexes tested.} Stars above the boxplots indicate statistically significant difference in mean maximum force relative to the WT complex.}
\end{figure}

\clearpage
\begin {table}[H]
\caption{\label{tab:summary_mutants}Summary of prior information available for each mutation tested. Observed $in~vivo$ refers to mutations that have been observed in rodent populations. Phenotype $in~vitro$ refers to the observed phenotype in $in~vitro$ viral entry assays.} 
\begin{center}
  \resizebox{11cm}{!} {
    \begin{tabular}{l c r r}
    \hline
      Mutation & Observed $in~vivo$ & Phenotype $in~vitro$ \\
            WT &                Yes &         Normal Entry \\
         N348A &                 No &                    - \\
         N348K &                Yes &     Diminished Entry \\
         N348W &                 No &                    - \\
         Y211A &                 No &        No Expression \\
         Y211D &                Yes &        No Expression \\
         Y211T &                 No &     Diminished Entry \\
        vR111A &                 No &     Diminished Entry \\
   N348A/Y211A &                 No &                    - \\
   N348W/Y211A &                 No &                    - \\
  vR111A/Y211A &                 No &                    - \\
    \hline
    \end{tabular}
  }
\end{center}
\end{table}
